A higher order approximate static condensation method for multi-material diffusion problems

### 2019-01-26 asc.tex
Add Maxim's changes

	\begin{abstract}
		The paper studies an approximate static condensation method for the diffusion problem with discontinuous diffusion coefficients. The method allows for a general polygonal mesh which is unfitted to the material interfaces. Moreover, the interfaces can be discontinuous across the mesh edges as typical for numerical reconstructions using the volume or moment-of-fluid methods.  We apply a mimetic finite difference method to solve local diffusion problems and use $P_1$ (mortar) edge elements to couple local problems into the global system. The condensation process and the properties of the resulting algebraic system are discussed. It is demonstrated that the method is second order accurate on smooth solutions and performs well for problems with high contrast in diffusion coefficients. Experiments also show the robustness with respect to position of the interface against the underlying mesh.
	\end{abstract}

@@

	Past decades evidenced an explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter. This includes immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches. Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.  If one applies a sharp representation to handle complex geometries or interfaces undergoing large deformations, it is convenient to allow the  interface to cut through the background mesh in an arbitrary way. In turn, this leads to the problem of building accurate and stable approximations for  so-called multi-material cells, i.e. the mesh cells intersected by material interfaces. In particular, one is interested in discretizations to be robust with respect to how interfaces intersect the mesh and to the contrast of  material properties, e.g. the ratio of physical parameters. This is the setting and the problem  we focus in this paper.

@@

As an alternative to the homogenization, one may reconstruct interfaces in each  multi-material cell  using a piecewise planar approximation. In this case, single-material domains  in the cell are  non-overlapping polytopes that typically preserve known material volumes.
%The alternatives generally require for the so-called interface reconstruction to be used in order to approximate material interfaces inside multi-material cells. Interface reconstruction methods typically represent materials in a cell by non-overlapping single-material polytopes that match given volume fractions.
%The most popular approach is based on using a single linear interface to represent an interface between two materials, and is commonly called the Piecewise-Linear Interface Calculation (PLIC). 
In this paper, we deal with interfaces reconstructed by the volume-of-fluid (VOF)~\cite{hirt1981volume} method, which is a commonly used numerical interface recovery approach. The approach includes the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} that generally provide better accuracy if centroids of material subdomains are known.
For the numerical experiments here we apply the extended MOF~\cite{kikinzon2018xmof}  to construct local meshes inside multi-material cells such that subcell contains only one material and all information about the local topology is available.
% MAxim: It was not clear why you particularly mention  X-MOF. So I assume that it is what you use for experiments.

%A drawback of interface reconstruction is that reconstructed material interfaces are discontinuous on the interfaces between multi-material cells.
The conservation properties of the  VOF and MOF approaches, however, come at a price of recovering a piecewise planar interface approximation that is  discontinuous across the faces of the background computational mesh.
One approach to deal with this issue is merging the local tessellations with the computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}. It appears to be a non-trivial computational geometry problem, and the resulting mesh in 2D typically contains very small and co-linear faces, while the extension of this approach to 3D does not seem feasible for general unstructured meshes.

@@

	Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively. $-\vect C_\mmesh$ is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
	to a vector from  $\mathbb{R}^{n_{f}}$.
	For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
	Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on all the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of function defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
	\[
		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
	\]

@@

	When the Lagrange multiplier space $\Lambda$ couples local MFD solutions, it is convenient to define
	degrees of freedom for $\lambda\in\Lambda$ in terms of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
	\begin{equation}\label{asc_dofs}
		\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
	\end{equation}
	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace[\bface]$-orthogonal polynomials of degree~$n$.

@@

	We define $\vect R_\mmesh$ locally for any fixed $\bcell\in\bmesh$. Let us enumerate all faces of the given $T$ by index $j$. For example, $j=1,\dots,4$ for the polygonal cell in Figure~\ref{fig:asc_dofs:asc1:mmc}. For each $j$, index $i$ enumerates mini-faces from $\mfaces[ext](T)$ belonging to the macro-face $j$. For example, $i\in\{1,2,3\}$ for $j=1$ and $i\in\{1\}$ for $j=4$ for the same example in Figure~\ref{fig:asc_dofs:asc1:mmc}. Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f. assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda^{(0)}_{j}(T)$, $\lambda^{(1)}_{j}(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc}) so that we have
	\begin{equation}\label{lambda_intermsof_moments}
		{\lambda}\big({\vect r}(t)\big) = \lambda^{(1)}_{j}(T)\,|F|\,t + \left( \lambda^{(0)}_{j}(T) - \frac{\lambda^{(1)}_{j}(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int]
	\end{equation}
	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.

@@

	Substituting~\eqref{asc_flux_lambda} into \eqref{eq:aux1} we get the local equation for~${\vect \lambda}_\bcell$
	\begin{align}\label{local_system}
		\begin{split}
			\Big( \underbrace{\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect A_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect R_{\mmesh^+} \right)}_{\vect S_{\bcell^+} \coloneqq} {\vect \lambda}_{\bcell^+} \Big)_i
			&+
			\Big( \underbrace{\left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect A_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect R_{\mmesh^-} \right)}_{\vect S_{\bcell^-} \coloneqq} {\vect \lambda}_{\bcell^-} \Big)_j = \\
			\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect a}_{\mmesh^+}}_{{\vect b}_{\bcell^+} \coloneqq} \big)_i
			&+
			\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect a}_{\mmesh^-}}_{{\vect b}_{\bcell^-} \coloneqq} \big)_j.
		\end{split}
	\end{align}
	As standard in finite element methods, one assembles the global system~\eqref{asc_system} from the local matrices and local right-hand side vectors.  Thus we may formally write
	\begin{align}\label{global_system_assembly}
		%\begin{split}
		\vect S_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell, \quad
		{\vect b}_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,{\vect b}_\bcell.
		%\end{split}
	\end{align}
	where $\vect N_\bcell$ defines global to local mapping for the cell $T$.

@@

	Now we show that the global matrix~$\vect S_\bmesh$ in~\eqref{asc_system} is symmetric and positive definite. We give the arguments for ASC(1). Same arguments hold for ASC(0) after obvious simplifications.
	\vskip .2cm
	%\begin{theorem}\label{thm:asc0}
	%		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(0)
	%	\end{theorem}
	%	\begin{proof}
	%		From~\eqref{asc0_interp} we have that for any cell~$\bcell$\,/\,its mini\,mesh~$\mmesh$ the interpolating matrix may be written as
	%		\begin{equation*}
	%			\vect R_\mmesh =
	%			\begin{pmatrix}
	%				{\vect e}_1 & & & \\
	%				& {\vect e}_2 & & \\
	%				& & \ddots & \\
	%				& & & {\vect e}_m
	%			\end{pmatrix},
	%		\end{equation*}
	%		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and ${\vect e}_k \coloneqq$ column vector of all ones; its length is the number of mini\,faces of the base\,face~$k$. Clearly, columns of~$\vect R_\mmesh$ are linearly independent.
	%		
	%	\end{proof}
	\begin{lemma}\label{thm:asc1}
		%If~$\bfaces_\bcell \cap \bfaces[\textnormal{mixed}] = \varnothing$, then~
		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(1)
	\end{lemma}
	\begin{proof}
		\vskip -.3cm
		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
		%that has no mixed base\,faces, ${\bfaces_\bcell \cap \bfaces[mixed] = \varnothing}$,
		the interpolating matrix may be written as
		\begin{equation}\label{r_wo_mixed}\footnotesize
			\vect R_\mmesh =
			\begin{pmatrix}
				\vect S_1 & & & \\
				& \vect S_2 & & \\
				& & \ddots & \\
				& & & \vect S_m
			\end{pmatrix},
		\end{equation}
		where~$m \coloneqq$ number of macro-faces spanning~$\bcell$ and
		\begin{equation*}
			\vect S_k \coloneqq
			\begin{cases}
				\begin{pmatrix}
					1 &  s_{k\,1} \\
					\vdots & \vdots \\
					1 &  s_{k\,m_k} \\
				\end{pmatrix}, & \text{if }k\text{th face is multi-material face}, \\
				1, & \text{otherwise},
			\end{cases}
		\end{equation*}
		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th macro-face. If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.

		Clearly, matrix~$\vect R_\mmesh$ has a non-trivial kernel iff
		\begin{equation*}
			s_{k\,i} =  s_{k\,j}, \quad i, j = 1, 2, \dots, m_k
		\end{equation*}
		for some~$k$. Take some $\vect S \equiv \vect S_k$ corresponding to a multi-material face~$F \in \bfaces_\bcell$ with~${l \coloneqq m_k}$ materials,
		\begin{equation*}
			\vect S = \begin{pmatrix}
				1 &  s_1 \\
				\vdots & \vdots \\
				1 &  s_l \\
			\end{pmatrix}.
		\end{equation*}
		It is sufficient to show that~$ s_1 \ne  s_2$. Let $f_1$ and $f_2$ be corresponding mini-faces. We have
		\[
			s_1 = \frac{1}{2}\left( |f_1| - |F| \right), \quad
			s_2 = |f_1| + \frac{1}{2}\left( |f_2| - |F| \right),
		\]
		and
		\begin{equation*}
			s_1 =  s_2 \quad\Leftrightarrow\quad |f_1| + |f_2| = 0.
		\end{equation*}
		Hence $ s_1 \ne  s_2$, and~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ follows.
	\end{proof}
	\vskip .3cm
	\begin{theorem}
		Matrix $\vect S_\bmesh$ is symmetric. If $c > 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
	\end{theorem}
	\begin{proof}
		\vskip -.3cm
		First, noting that for any two symmetric positive definite matrices $\vect A_1$ and $\vect A_2$ inequality $\vect A_1 \ge \vect A_2$ implies $\vect A_1^{-1} \le \vect A_2^{-1}$, we conclude
		\begin{equation}\label{aux2}
			\widetilde{\vect B}^T \left( \vect \Sigma+ \widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B}
			\le
			\widetilde{\vect B}^T \left(\widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B} \le \vect I,
		\end{equation}
		where $\vect \Sigma$ is any symmetric and non-negative definite matrix, $\widetilde{\vect B}$ is any matrix such that \\ ${\Ker\widetilde{\vect B}^T = \{ \vect 0 \}}$, and $\vect I$ is identity matrix. To check the last inequality in~\eqref{aux2}, one can consider, e.g., the SVD decomposition of $\widetilde{\vect B}$.

>>>>

	\begin{abstract}
		The paper studies an approximate static condensation method for the diffusion problem with discontinuous diffusion coefficients. The method allows for a general polygonal mesh which is unfitted to the material interfaces. Moreover, the interfaces can be discontinuous across the mesh edges as typical for numerical reconstructions using the volume or moment-of-fluid methods.  We apply a mimetic finite difference method to solve local diffusion problems and use $P_1$ (mortar) edge elements to couple local problems into the global system. The condensation process and the properties of the resulting algebraic system are discussed. It is demonstrated that the method is second order accurate on smooth solutions and performs well for problems with high contrast in diffusion coefficients. Experiments also show the robustness with respect to position of the material interfaces against the underlying mesh.
	\end{abstract}

@@

	Past decades evidenced an explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter. These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches. Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.  If one applies a sharp representation to handle complex geometries or interfaces undergoing large deformations, it is convenient to allow the  interface to cut through the background mesh in an arbitrary way. In turn, this leads to the problem of building accurate and stable approximations for  so-called multi-material cells, i.e. the mesh cells intersected by material interfaces. In particular, one is interested in discretizations which are robust with respect to how interfaces intersect the mesh and with respect to the contrast of  material properties, e.g. the ratio of physical parameters. This is the setting and the problem  we focus in this paper.

@@

As an alternative to the homogenization, one may reconstruct interfaces in each  multi-material cell  using a piecewise planar approximation. In this case, single-material domains  in the cell are  non-overlapping polytopes that typically preserve known material volumes.
%The alternatives generally require for the so-called interface reconstruction to be used in order to approximate material interfaces inside multi-material cells. Interface reconstruction methods typically represent materials in a cell by non-overlapping single-material polytopes that match given volume fractions.
%The most popular approach is based on using a single linear interface to represent an interface between two materials, and is commonly called the Piecewise-Linear Interface Calculation (PLIC).
In this paper, we deal with interfaces reconstructed by the volume-of-fluid (VOF)~\cite{hirt1981volume} method, which is a commonly used numerical  approach to recover interface location. The approach includes the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} that generally provide better accuracy if centroids of material subdomains are known.
For the numerical experiments here we apply the extended MOF~\cite{kikinzon2018xmof}  to construct local meshes inside multi-material cells such that subcell contains only one material and all information about the local topology is available.
% MAxim: It was not clear why you particularly mention  X-MOF. So I assume that it is what you use for experiments.

%A drawback of interface reconstruction is that reconstructed material interfaces are discontinuous on the interfaces between multi-material cells.
The conservation properties of the  VOF and MOF approaches, however, come at a price of recovering a piecewise planar interface approximation that is  discontinuous across the faces of the background computational mesh.
One technique to deal with this issue consists in including the local tessellations into the global computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}. This turns out to be a non-trivial computational geometry problem, and the resulting mesh in 2D often contains very small and co-linear faces, while the extension of this approach to 3D does not seem feasible for general unstructured meshes.

@@

	Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; $-\vect C_\mmesh$ is a diagonal scaling matrix, i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
	to a vector from  $\mathbb{R}^{n_{f}}$.
	For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
	Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
	\[
		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
	\]

@@

	When the Lagrange multiplier space $\Lambda$ couples local MFD solutions, it is convenient to define
	degrees of freedom for $\lambda\in\Lambda$ in terms of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
	\begin{equation}\label{asc_dofs}
		\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
	\end{equation}
	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace$-orthogonal polynomials on $F$ of degree~$n$.

@@

	We define $\vect R_\mmesh$ locally for any fixed $\bcell\in\bmesh$. Let us enumerate all faces of the given $T$ by index $j$. For example, $j=1,\dots,4$ for the polygonal cell in Figure~\ref{fig:asc_dofs:asc1:mmc}. For each $j$, index $i$ enumerates mini-faces from $\mfaces[ext](T)$ belonging to the macro-face $j$. For example, $i\in\{1,2,3\}$ for $j=1$ and $i\in\{1\}$ for $j=4$ for the same example in Figure~\ref{fig:asc_dofs:asc1:mmc}. Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f. assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda^{(0)}_{j}(T)$, $\lambda^{(1)}_{j}(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc}) so that we have
	\begin{equation}\label{lambda_intermsof_moments}
		{\lambda}\big({\vect r}(t)\big) = \lambda^{(1)}_{j}(T)\,|F|\,t + \left( \lambda^{(0)}_{j}(T) - \frac{\lambda^{(1)}_{j}(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int]
	\end{equation}
	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of the face $F$ with index $j$ among macro-faces of $T$.

@@

	Substituting~\eqref{asc_flux_lambda} into \eqref{eq:aux1} we get the local equation for~${\vect \lambda}_\bcell$
	\begin{align}\label{local_system}
		\begin{split}
			\Big( \underbrace{\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect A_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect R_{\mmesh^+} \right)}_{\vect S_{\bcell^+} \coloneqq} {\vect \lambda}_{\bcell^+} \Big)_i
			&+
			\Big( \underbrace{\left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect A_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect R_{\mmesh^-} \right)}_{\vect S_{\bcell^-} \coloneqq} {\vect \lambda}_{\bcell^-} \Big)_j = \\
			\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect a}_{\mmesh^+}}_{{\vect b}_{\bcell^+} \coloneqq} \big)_i
			&+
			\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect a}_{\mmesh^-}}_{{\vect b}_{\bcell^-} \coloneqq} \big)_j.
		\end{split}
	\end{align}
	As standard in finite element methods, one assembles the global system~\eqref{asc_system} from the local matrices and local right-hand side vectors.  Thus we may formally write
	\begin{align}\label{global_system_assembly}
		%\begin{split}
		\vect S_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell, \quad
		{\vect b}_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,{\vect b}_\bcell,
		%\end{split}
	\end{align}
	where $\vect N_\bcell$ defines global to local mapping for the cell $T$.

@@

	Now we show that the global matrix~$\vect S_\bmesh$ in~\eqref{asc_system} is symmetric and positive definite. We give the arguments for ASC(1). Same arguments hold for ASC(0) after obvious simplifications.
	\vskip .2cm
	%\begin{theorem}\label{thm:asc0}
	%		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(0)
	%	\end{theorem}
	%	\begin{proof}
	%		From~\eqref{asc0_interp} we have that for any cell~$\bcell$\,/\,its mini\,mesh~$\mmesh$ the interpolating matrix may be written as
	%		\begin{equation*}
	%			\vect R_\mmesh =
	%			\begin{pmatrix}
	%				{\vect e}_1 & & & \\
	%				& {\vect e}_2 & & \\
	%				& & \ddots & \\
	%				& & & {\vect e}_m
	%			\end{pmatrix},
	%		\end{equation*}
	%		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and ${\vect e}_k \coloneqq$ column vector of all ones; its length is the number of mini\,faces of the base\,face~$k$. Clearly, columns of~$\vect R_\mmesh$ are linearly independent.
	%		
	%	\end{proof}
	\begin{lemma}\label{thm:asc1}
		%If~$\bfaces_\bcell \cap \bfaces[\textnormal{mixed}] = \varnothing$, then~
		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(1)
	\end{lemma}
	\begin{proof}
		\vskip -.3cm
		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
		%that has no mixed base\,faces, ${\bfaces_\bcell \cap \bfaces[mixed] = \varnothing}$,
		the interpolating matrix may be written as
		\begin{equation}\label{r_wo_mixed}\footnotesize
			\vect R_\mmesh =
			\begin{pmatrix}
				\vect S_1 & & & \\
				& \vect S_2 & & \\
				& & \ddots & \\
				& & & \vect S_m
			\end{pmatrix},
		\end{equation}
		where~$m \coloneqq$ number of macro-faces spanning~$\partial\bcell$ and
		\begin{equation*}
			\vect S_k \coloneqq
			\begin{cases}
				\begin{pmatrix}
					1 &  s_{k\,1} \\
					\vdots & \vdots \\
					1 &  s_{k\,m_k} \\
				\end{pmatrix}, & \text{if }k\text{th face is multi-material face}, \\
				1, & \text{otherwise},
			\end{cases}
		\end{equation*}
		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th macro-face. If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.

		Clearly, matrix~$\vect R_\mmesh$ has a non-trivial kernel iff
		\begin{equation*}
			s_{k\,i} =  s_{k\,j}, \quad i, j = 1, 2, \dots, m_k
		\end{equation*}
		for some~$k$. Take some $\vect S = \vect S_k$ corresponding to a multi-material face~$F \in \bfaces_\bcell$ with~${l \coloneqq m_k}$ materials,
		\begin{equation*}
			\vect S = \begin{pmatrix}
				1 &  s_1 \\
				\vdots & \vdots \\
				1 &  s_l \\
			\end{pmatrix}.
		\end{equation*}
		It is sufficient to show that~$ s_1 \ne  s_2$. Let $f_1$ and $f_2$ be corresponding mini-faces. We have
		\[
			s_1 = \frac{1}{2}\left( |f_1| - |F| \right), \quad
			s_2 = |f_1| + \frac{1}{2}\left( |f_2| - |F| \right),
		\]
		and
		\begin{equation*}
			s_1 =  s_2 \quad\Leftrightarrow\quad |f_1| + |f_2| = 0.
		\end{equation*}
		Hence $ s_1 \ne  s_2$, and~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ follows.
	\end{proof}
	\vskip .3cm
	\begin{theorem}
		Matrix $\vect S_\bmesh$ is symmetric. If $c > 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
	\end{theorem}
	\begin{proof}
		\vskip -.3cm
		First, noting that for any two symmetric positive definite matrices $\vect A_1$ and $\vect A_2$ inequality $\vect A_1 \ge \vect A_2$ implies $\vect A_1^{-1} \le \vect A_2^{-1}$, we conclude
		\begin{equation}\label{aux2}
			\widetilde{\vect B}^T \left( \vect \Sigma+ \widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B}
			\le
			\widetilde{\vect B}^T \left(\widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B} \le \vect I,
		\end{equation}
		where $\vect \Sigma$ is any symmetric and non-negative definite matrix, $\widetilde{\vect B}$ is any matrix such that \\ ${\Ker\widetilde{\vect B}^T = \{ \vect 0 \}}$, and $\vect I$ is identity matrix. To check the last inequality in~\eqref{aux2}, one can consider, e.g., the SVD decomposition of $\widetilde{\vect B}$.
